Data for ms. 1

### 2017-04-13 ms1/ms1.Rmd
updated ms1

```{r analyze_function}
age_group_f = function(x) bounds_group(x, c(66, 70, 75, 80, 85, 90, 95, 100))
claims_group_f = function(x) bounds_group(x, c(0, 1, 2, 5, 10, 20, Inf))

@@

chars_by_age_group = data_by_field('claims_by_age_group') %>%
  mutate(cpkp=round(cpkp), mean_n_cc=round(mean_n_cc, digits=2)) %>%
  select(age_group, year, cpkp, mean_n_cc) %>%
  gather('variable', 'value', cpkp, mean_n_cc) %>%
  mutate(variable=interaction(year, variable)) %>%
  select(-year) %>%
  spread(variable, value) %T>%
  write_tsv('tables/supptable1_age_group.tsv') %>%
  kable

>>>>

```{r analyze_function}
age_group_f = function(x) bounds_group(x, c(65, 70, 75, 80, 85, 90, 95, 100))
claims_group_f = function(x) bounds_group(x, c(0, 1, 2, 5, 10, 20, Inf))

@@

chars_by_age_group = data_by_field('chars_by_age_group') %>%
  mutate(cpkp=round(cpkp), mean_n_cc=round(mean_n_cc, digits=2)) %>%
  select(age_group, year, cpkp, mean_n_cc) %T>%
  write_tsv('tables/data_age_group.tsv')
